Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-12-15 SEIR.tex
deal with comments

Age-based contact patterns are important for the transmission dynamics of respiratory diseases~\autocites{birrellBayesian}{jacksonEffects}.
Respiratory diseases can be spread by conversational contacts, which show very clear age patterns (see \cref{SEIR:fig:age-contacts}).
In particular, the contacts are \emph{associative} (contacts are more likely between individuals of similar ages) and younger age groups have more contacts; this will tend to concentrate the epidemic in these younger age groups~\autocite[67]{keelingModeling}.
\begin{figure}
  \centering \includegraphics[width=\textwidth]{SEIR/contact_matrices}
  \caption[Age-based contact matrices]{Number of contacts reported between age groups in two contact surveys: (A) number of contacts reported in the POLYMOD survey~\autocite{mossongSocial}; (B) number of contacts reported in the BBC Pandemic survey~\autocite{klepacContacts}, which only collected data on those aged over 12. A clear diagonal, showing associative mixing is visible, and children have more contacts. Parallel diagonals off the main diagonal show mixing between parents and their children. Figure adapted from \textcite{klepacContacts}, licensed under CC BY-NC-ND 4.0.}
  \label{SEIR:fig:age-contacts}
\end{figure}

@@

\todo[inline]{discuss comparisons with the backcalculation, based on notes below (using preliminary results)}

\begin{itemize}
    \item Results here disagree with previous chapter's results.
    \item The model in previous chapter is more flexible than here, showing the limitations discussed above. Previous chapter fits better.
    \item The previous chapter's modelling benefits from being able to use flexible approximate inference methods that scale to many parameters, including random effects. Here, I am limited by the inference procedure. MCMC was unable to scale to the full model used in the previous chapter, which has a computationally cheaper likelihood as it is a GLM, not requiring solving an ODE.
    \item Shows that there is a lot of information in the data which could be exploited by a suitably flexible mechanistic model. Such a model would be useful for policy-decisions because it could infer where transmission is occurring (\eg in schools or workplaces) and how this changes over time.
    \item The narrower credible intervals in this chapter are a realisation of the standard bias-variance tradeoff. By making stronger assumptions regarding how transmission occurs, the variance is reduced. However, if these assumptions are incorrect (which is almost certainly the case), bias occurs.
\end{itemize}

>>>>

Age-based contact patterns are important for the transmission dynamics of respiratory diseases~\autocites{birrellBayesian}{jacksonEffects}.
Respiratory diseases can be spread by conversational contacts, which show very clear age patterns (see \cref{SEIR:fig:age-contacts}).
In particular, the contacts are \emph{associative} (contacts are more likely between individuals of similar ages) and younger age groups have more contacts; this will tend to concentrate the epidemic in these younger age groups~\autocite[67]{keelingModeling}.
\begin{figure}
  \centering \includegraphics[width=\textwidth]{SEIR/contact_matrices}
  \caption[Age-based contact matrices]{Number of contacts reported between age groups in two contact surveys: (A) number of contacts reported in the POLYMOD survey~\autocite{mossongSocial}; (B) number of contacts reported in the BBC Pandemic survey~\autocite{klepacContacts}, which only collected data on those aged over 12. A clear diagonal, showing associative mixing is visible, and children have more contacts. Parallel diagonals off the main diagonal show mixing between parents and their children. Figure adapted from \textcite{klepacContacts}.}
  \label{SEIR:fig:age-contacts}
\end{figure}

@@

\todo[inline]{discuss comparisons with the backcalculation}
